Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
removed 2 references for space considerations (authors were ref'd twice)

Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.

\section{Conclusions and future work}
%\todo[inline]{Need to juxtapose our work against previous work -- contribution}
\todo[inline]{tighten... typically conclusions are much shorter.}

>>>>

%Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. 
% this reduces the line length and drops a ref even though we still have a scacchi kickin around
Massey~\cite{massey02icse} and Scacchi~\cite{scacchi05b} looked at the topic of requirements in open-source software. 
Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

% XXX vanity or space.. 
% Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.

\section{Conclusions and future work}
%\todo[inline]{Need to juxtapose our work against previous work -- contribution}
%\todo[inline]{tighten... typically conclusions are much shorter.}
